---
output:
  reprex::reprex_document:
    venue: "gh"
    advertise: FALSE
    session_info: TRUE
    style: TRUE
    comment: "#;-)"
    tidyverse_quiet: FALSE
    std_out_err: TRUE
knit: reprex::reprex_render
---

This template demonstrates many of the bells and whistles of the `reprex::reprex_document()` output format. The YAML sets many options to non-default values, such as using `#;-)` as the comment in front of output.

## Code style

Since `style` is `TRUE`, this difficult-to-read code (look at the `.Rmd` source file) will be restyled according to the Tidyverse style guide when it's rendered. Whitespace rationing is not in effect!

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stringr, readxl, data.table, gdata)

library(dplyr)
library(pacman)
library(cobalt)

# install matching package
library(Matching)

# install packages that can use glm function

```

```{r}
# import data/output/HCRIS_2012.csv
final.hcris <- read.csv("data/output/HCRIS_Data_2012.csv")
```

```{r}
lp.vars <- final.hcris %>% 
  dplyr::select(beds_1, beds_2, penalty, beds_3,
         beds_4, price) %>%
  filter(complete.cases(.))
lp.covs <- lp.vars %>% dplyr::select(-c("penalty","price"))

```

# without adjustment

```{r}
love.plot(bal.tab(lp.covs,treat=lp.vars$penalty), colors="black", shapes="circle", threshold=0.1) + 
  theme_bw() + theme(legend.position="none")
```

# single inverse variance weighting

```{r}
m.nn.var <- Matching::Match(Y=lp.vars$price,
                             Tr=lp.vars$penalty,
                             X=lp.covs,
                             M=1,   #<<
                             Weight=1,
                             estimand="ATE")

summary(m.nn.var)


v.name=data.frame(new=c("Q1","Q2", "Q3",
                   "Q4"))


# save the plot in a variable
var_plot <- love.plot(bal.tab(m.nn.var, covs = lp.covs, treat = lp.vars$penalty), 
          threshold=0.1, 
          var.names=v.name,
          grid=FALSE, sample.names=c("Unmatched", "Matched"),
          position="top", shapes=c("circle","triangle"),
          colors=c("black","blue")) + 
  theme_bw()


# save the plot in the local directory
ggsave("var_plot.png", var_plot, width=10, height=10, units="cm")


```


# single Mahalanobis distance matching

```{r}
m.nn.md <- Matching::Match(Y=lp.vars$price,
                           Tr=lp.vars$penalty,
                           X=lp.covs,
                           M=1,
                           Weight=2,
                           estimand="ATE")  

summary(m.nn.md)

# save the plot in a variable
md_plot <- love.plot(bal.tab(m.nn.md, covs = lp.covs, treat = lp.vars$penalty), 
          threshold=0.1, 
          var.names=v.name,
          grid=FALSE, sample.names=c("Unmatched", "Matched"),
          position="top", shapes=c("circle","triangle"),
          colors=c("black","blue")) + 
  theme_bw()

# save the plot in the local directory
ggsave("md_plot.png", md_plot, width=10, height=10, units="cm")


```

# propensity score matching

```{r}
logit.model <- glm(penalty ~ beds_1 + beds_2 + beds_3 + beds_4, family=binomial, data=lp.vars)
ps <- fitted(logit.model)
m.nn.ps <- Matching::Match(Y=lp.vars$price,
                           Tr=lp.vars$penalty,
                           X=ps,
                           M=1,
                           estimand="ATE")

# show the matching_est 

summary(m.nn.ps)


# save the plot in a variable
ps_plot <- love.plot(bal.tab(m.nn.ps, covs = lp.covs, treat = lp.vars$penalty), 
          threshold=0.1, 
          var.names=v.name,
          grid=FALSE, sample.names=c("Unmatched", "Matched"),
          position="top", shapes=c("circle","triangle"),
          colors=c("black","blue")) + 
  theme_bw()

# save the plot in the local directory
ggsave("ps_plot.png", ps_plot, width=10, height=10, units="cm")

```

# linear regression (two step)

```{r}
reg1.dat <- lp.vars %>% filter(penalty==1, complete.cases(.))
reg1 <- lm(price ~ beds_1 + beds_2 + beds_3 + beds_4, data=reg1.dat)

reg0.dat <- lp.vars %>% filter(penalty==0, complete.cases(.))
reg0 <- lm(price ~ beds_1 + beds_2 + beds_3 + beds_4, data=reg0.dat)
pred1 <- predict(reg1,new=lp.vars)
pred0 <- predict(reg0,new=lp.vars)

mean(pred1-pred0)
```


```{r}
# another linear regression with penalty and beds_1 to beds_4 as covariates and include the interaction term bewteen penalty and (x_i-x_bar) for each beds
reg2.dat <- lp.vars %>% filter(complete.cases(.))

# in reg2.dat, create four new variables, var_1, var_2, var_3, var_4, which are the difference between beds_1 to beds_4 and their mean
reg2.dat$var_1 <- reg2.dat$beds_1 - mean(reg2.dat$beds_1)
reg2.dat$var_2 <- reg2.dat$beds_2 - mean(reg2.dat$beds_2)
reg2.dat$var_3 <- reg2.dat$beds_3 - mean(reg2.dat$beds_3)
reg2.dat$var_4 <- reg2.dat$beds_4 - mean(reg2.dat$beds_4)


reg2 <- lm(price ~ beds_1 + beds_2 + beds_3 + beds_4 + penalty + var_1:penalty + var_2:penalty + var_3:penalty + var_4:penalty, data=reg2.dat)

summary(reg2)



# extract the se of the coefficient of penalty
se.penalty <- summary(reg2)$coefficients[5,2]
se.penalty


library(tidyverse)
library(broom)

reg2_sum <- tidy(reg2)
reg2_sum

# class of reg2_sum
class(reg2_sum)

```



# in one table
```{r}
summary(m.nn.var)
summary(m.nn.md)
summary(m.nn.ps)
mean(pred1-pred0)


# create a table showing the ATE for each method
sum_table <- data.frame("Method" = c("Single Inverse Variance Weighting", "Single Mahalanobis Distance Matching", "Propensity Score Matching", "Linear Regression (Two Step)"),
                    "ATE" = c(m.nn.var$est
                                ,m.nn.md$est
                                ,m.nn.ps$est
                                ,mean(pred1-pred0)),
                    "Standard Error" = c(m.nn.var$se
                                         ,m.nn.md$se
                                         ,m.nn.ps$se
                                         ,se.penalty))


sum_table

```

# save in the workspace (python&R)
```{r}
save(sum_table, reg2_sum, file="matching_est.RData")

```

# quesiton 8, 9, 10

# qmd file

# transfer to econ470_hwk2 file


